### 2016-06-06 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream report figures and content

\begin{figure}[!ht]
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/NF_example}
		\caption{Narrow fog stream from combination nozzle}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/WF_example}
		\caption{Wide fog stream from combination nozzle}
	\end{subfigure}
	\\~\\
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SS_70}
		\caption{Straight stream from combination nozzle}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
		\caption{Solid stream from smooth bore nozzle with 1~tip}
	\end{subfigure}
	\caption[Hose stream patterns used during experiments.]{The four types of hose stream patterns used during water flow experiments.}
	\label{fig:hose_streams}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
	\caption[Plan view of the Single Story Structure setup for Tests 1 and 5.]{Plan view of the Single Story Structure setup for Tests 1 and 5. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square). The north side double doors remained opened for the entire duration of the experiments.}
	\label{fig:east_setup}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
	\caption[Plan view of the Two Story Structure setup for Tests 2 and 6.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 2 and 6. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square). The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
	\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
	\caption[Plan view of the Two Story Structure setup for Tests 3 and 7.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 3, 4, and 7. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square). The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
	\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\subsubsection{Test 1}
Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}). A plan view of the structure's layout during Test~1 can be found in Fig.~\ref{fig:east_setup}. The figure highlights the general direction of the established flow path along with the approximate location of A6, the bi-directional probe array used to measure gas velocity through the northeast interior doorway. The procedure for Test~1 was the simplest of all the test procedures. First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds. The procedure was repeated an additional time.

\begin{figure}[!ht]
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/SS_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/NF_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test 1 in the Single Story Structure.}
	\label{fig:test_1_pic}
\end{figure}

\subsubsection{Tests 2 \& 3}
Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure. The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. This entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_2_3_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during Tests 2 and 3 in the Two Story Structure.}
	\label{fig:test_2_3_pic}
\end{figure}
\FloatBarrier

\subsubsection{Test 4}
Test 4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests 2 and 3. The stairwell door was opened for the entire experiment. The test began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop water flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Next, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated for the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test 4.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_70}
	\end{center} 
	\endminipage
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SB_70}
	\end{center}
	\endminipage
	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 4.}
	\label{fig:test_4_pic}
\end{figure}
\FloatBarrier

\subsection{Handline Experiments}
\label{sec:handline_procedure}
Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream. One test, Test 5, occurred in the Single Story Structure, and the remaining tests, Tests 6 and 7, occurred in the Two Story Structure. All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.

\subsubsection{Test 5}
Test 5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}). The layout of the structure was identical to the layout for Test 1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}. The procedure for Test 5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position. After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the nozzle was aimed at the south doorway of Room B, and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern. The procedure was repeated using a narrow fog stream and a wide fog stream. This entire process was repeated for the streams being applied in the fixed and counterclockwise patterns.

\begin{figure}[!ht]
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/SS_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/NF_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 5.}
	\label{fig:test_5_pic}
\end{figure}

\subsubsection{Tests 6 \& 7}
Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.

\begin{figure}[!ht]
	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
	\caption[North side of Two Story Structure containing a fully established flow path during Test 6.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 6.}
	\label{fig:test_6_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test 2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
	\label{fig:Test_2_BDP_A10_Avg_All}
\end{figure}

@@

Looking at the table and figures, a number of trends can be observed. For example, there was significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1. Looking at Table~\ref{table:all_mon_vel_avgs}, the narrow fog and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream. This trend can also be seen graphically in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}. Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
\FloatBarrier

\section{Handline Experiments}
\label{sec:handline_results}
Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test 6. Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6--7, respectively.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test 6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 6 for the three hose stream patterns.}
	\label{fig:Test_6_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/NF_example}
		\caption{Narrow fog stream from combination nozzle}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/WF_example}
		\caption{Wide fog stream from combination nozzle}
	\end{subfigure}
	\\~\\
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SS_70}
		\caption{Straight stream from combination nozzle}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\columnwidth}
		\centering
		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
		\caption{Solid stream from 1~in smooth bore nozzle}
	\end{subfigure}
	\caption[Hose stream patterns used during experiments.]{The four types of hose stream patterns used during water flow experiments.}
	\label{fig:hose_streams}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
	\caption[Plan view of the Single Story Structure setup for Tests~1 and 5.]{Plan view of the Single Story Structure setup for Tests~1 and 5. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square). The north side double doors remained opened for the entire duration of the experiments.}
	\label{fig:east_setup}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
	\caption[Plan view of the Two Story Structure setup for Tests~2 and 6.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests~2 and 6. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square). The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
	\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
	\caption[Plan view of the Two Story Structure setup for Tests~3 and 7.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests~3, 4, and 7. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square). The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
	\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\subsubsection{Test~1}
Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}). A plan view of the structure's layout during Test~1 can be found in Fig.~\ref{fig:east_setup}. The figure highlights the general direction of the established flow path along with the approximate location of A6, the bi-directional probe array used to measure gas velocity through the northeast interior doorway. The procedure for Test~1 was the simplest of all the test procedures. First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds. The procedure was repeated an additional time.

\begin{figure}[!ht]
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/SS_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/NF_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test~1 in the Single Story Structure.}
	\label{fig:test_1_pic}
\end{figure}

\subsubsection{Tests~2 \& 3}
Tests~2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure. The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. This entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_2_3_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during Tests~2 and 3 in the Two Story Structure.}
	\label{fig:test_2_3_pic}
\end{figure}
\FloatBarrier

\subsubsection{Test~4}
Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3. The stairwell door was opened for the entire experiment. The test began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop water flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Next, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated for the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test~4.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_70}
	\end{center} 
	\endminipage
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SB_70}
	\end{center}
	\endminipage
	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test~4.}
	\label{fig:test_4_pic}
\end{figure}
\FloatBarrier

\subsection{Handline Experiments}
\label{sec:handline_procedure}
Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream. One test, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure. All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.

\subsubsection{Test~5}
Test~5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}). The layout of the structure was identical to the layout for Test~1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}. The procedure for Test~5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position. After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the nozzle was aimed at the south doorway of Room B, and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern. The procedure was repeated using a narrow fog stream and a wide fog stream. This entire process was repeated for the streams being applied in the fixed and counterclockwise patterns.

\begin{figure}[!ht]
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/SS_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/NF_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test~5.}
	\label{fig:test_5_pic}
\end{figure}

\subsubsection{Tests~6 \& 7}
Tests~6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test~6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test~7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.

\begin{figure}[!ht]
	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
	\caption[North side of Two Story Structure containing a fully established flow path during Test~6.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test~6.}
	\label{fig:test_6_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test~2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~2 for the three hose stream patterns.}
	\label{fig:Test_2_BDP_A10_Avg_All}
\end{figure}

@@

Looking at the table and figures, a number of trends can be observed. For example, there was significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1. Looking at Table~\ref{table:all_mon_vel_avgs}, the narrow fog and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream. This trend can also be seen graphically in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}. Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test~4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
\FloatBarrier

\section{Handline Experiments}
\label{sec:handline_results}
Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test~6. Similar plots of the average measured velocity through the interior doorway for Tests~5 and 7 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test~5 and Tests~6--7, respectively.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test~6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~6 for the three hose stream patterns.}
	\label{fig:Test_6_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lcccc}
\toprule
 &  & \multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
\\ \midrule
 & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$)  
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}
